---
title: "i0008-beh-data"
editor: visual
execute:
  echo: true
  warning: false
  error: true
  collapse: true
format:
  html:
    embed-resources: true
    toc: true
    toc-depth: 4
    toc-expand: 4
    toc-title: Contents
    html-math-method: katex
    css: styles.css
    code-fold: true
    code-overflow: scroll
    code-line-numbers: true
    code-copy: true
    code-link: true
    code-tools: true
    grid: 
      body-width: 1000px
      sidebar-width: 10px
      margin-width: 450px
---

# Overview 

[View Color-Coded Results](./data/i0002-out/all-models-r1002-result-ALL.html)

# Init

```{r}
rm(list = ls(all = TRUE))
options(tidyverse.quiet = TRUE)
library(plyr)
library(tidyverse)
library(RColorBrewer)
```

# Data

```{r}
ifd0 <- "data/i0001-src"
ofd0 <- "data/i0002-out"
dir.create(ofd0, showWarnings=FALSE, recursive=TRUE)
ifn0 <- "jgnb-df9u.csv"
suppressWarnings(rm(list=ls(pattern="^df")))
df0 <- readr::read_csv(
  file = file.path(ifd0, ifn0),
  show_col_types = FALSE,
  col_types =  list(
     Sub = col_factor(),
     Ses = col_factor(),
     Run = col_factor(),
     Chrono = col_factor(),
     Condit = col_factor(),
     Gender = col_factor(),
     Education = col_factor(),
     TP = col_integer(),
     FP = col_integer(),
     TN = col_integer(),
     FN = col_integer(),
     NiiAcqTime = col_character(), ## col_time(format = ""),
     NiiAcqTIME = col_character(),
     LogFileTime = col_character(),
     .default = col_guess()),
  ) %>%
  dplyr::filter(Run %in% c("01", "02", "03")) %>%
  identity()

df0 %>% dim()
```

# Factor Levels

```{r}
df2 <- df0 %>%
  mutate(
    Ses = factor(Ses, levels=c("Morning", "Evening")),
    Run = factor(Run, levels=c("02", "01", "03")),
    Chrono = factor(Chrono, levels = c("Morning", "Evening")),
    Condit = factor(Condit, levels = c("Congruent", "Incongruent")),
  ) %>%
  mutate(
    NumBack = as.integer(NumBack),
    NumBack = paste0("n", sprintf("%02d", NumBack)),
    NumBack = factor(NumBack, levels = c("n02", "n01", "n03")),
  ) %>%
  identity()

df0 %>% dim()
df2 %>% dim()
```

# Models

```{r}
REML <- TRUE
control <- lme4::lmerControl(optimizer = "Nelder_Mead")

fit.RT    = lmerTest::lmer(formula=RT    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.TP    = lmerTest::lmer(formula=TP    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FP    = lmerTest::lmer(formula=FP    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.TN    = lmerTest::lmer(formula=TN    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FN    = lmerTest::lmer(formula=FN    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.Accur = lmerTest::lmer(formula=Accur ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Sensi = lmerTest::lmer(formula=Sensi ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Speci = lmerTest::lmer(formula=Speci ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Preci = lmerTest::lmer(formula=Preci ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.FPR   = lmerTest::lmer(formula=FPR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FNR   = lmerTest::lmer(formula=FNR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FDR   = lmerTest::lmer(formula=FDR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.NPV   = lmerTest::lmer(formula=NPV   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FOR   = lmerTest::lmer(formula=FOR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
```

# Save Models

```{r}
readr::write_rds(fit.RT,     file.path(ofd0, "fit.RT.rds"))
readr::write_rds(fit.TP,     file.path(ofd0, "fit.TP.rds"))
readr::write_rds(fit.FP,     file.path(ofd0, "fit.FP.rds"))
readr::write_rds(fit.TN,     file.path(ofd0, "fit.TN.rds"))
readr::write_rds(fit.FN,     file.path(ofd0, "fit.FN.rds"))
readr::write_rds(fit.Accur,  file.path(ofd0, "fit.Accur.rds"))
readr::write_rds(fit.Sensi,  file.path(ofd0, "fit.Sensi.rds"))
readr::write_rds(fit.Speci,  file.path(ofd0, "fit.Speci.rds"))
readr::write_rds(fit.Preci,  file.path(ofd0, "fit.Preci.rds"))
readr::write_rds(fit.FPR,    file.path(ofd0, "fit.FPR.rds"))
readr::write_rds(fit.FNR,    file.path(ofd0, "fit.FNR.rds"))
readr::write_rds(fit.FDR,    file.path(ofd0, "fit.FDR.rds"))
readr::write_rds(fit.NPV,    file.path(ofd0, "fit.NPV.rds"))
readr::write_rds(fit.FOR,    file.path(ofd0, "fit.FOR.rds"))
```

# Read Models

```{r}
fit.RT    <- readr::read_rds(file.path(ofd0, "fit.RT.rds"))
fit.TP    <- readr::read_rds(file.path(ofd0, "fit.TP.rds"))
fit.FP    <- readr::read_rds(file.path(ofd0, "fit.FP.rds"))
fit.TN    <- readr::read_rds(file.path(ofd0, "fit.TN.rds"))
fit.FN    <- readr::read_rds(file.path(ofd0, "fit.FN.rds"))
fit.Accur <- readr::read_rds(file.path(ofd0, "fit.Accur.rds"))
fit.Sensi <- readr::read_rds(file.path(ofd0, "fit.Sensi.rds"))
fit.Speci <- readr::read_rds(file.path(ofd0, "fit.Speci.rds"))
fit.Preci <- readr::read_rds(file.path(ofd0, "fit.Preci.rds"))
fit.FPR   <- readr::read_rds(file.path(ofd0, "fit.FPR.rds"))
fit.FNR   <- readr::read_rds(file.path(ofd0, "fit.FNR.rds"))
fit.FDR   <- readr::read_rds(file.path(ofd0, "fit.FDR.rds"))
fit.NPV   <- readr::read_rds(file.path(ofd0, "fit.NPV.rds"))
fit.FOR   <- readr::read_rds(file.path(ofd0, "fit.FOR.rds"))
```

# Tabulate Models

[View Color-Coded Results](./data/i0002-out/all-models-r1002-result-ALL.html)

```{r}
sjPlot::tab_model(
  fit.RT,
  fit.TP, fit.FP, fit.TN, fit.FN,
  fit.Accur,
  fit.Sensi,
  fit.Speci,
  fit.Preci,
  fit.FPR,
  fit.FNR,
  fit.FDR,
  fit.NPV,
  fit.FOR,
  show.reflvl = FALSE,
  show.intercept = TRUE,
  show.p = FALSE,
  wrap.labels = 888,
  p.style = "numeric_stars",
  # file = file.path(ofd0, "all-models-i0002-ALL.html"),
  dv.labels = c(
    "fit.RT",
    "fit.TP", "fit.FP", "fit.TN", "fit.FN",
    "fit.Accur",
    "fit.Sensi",
    "fit.Speci",
    "fit.Preci",
    "fit.FPR",
    "fit.FNR",
    "fit.FDR",
    "fit.NPV",
    "fit.FOR"))
```

# Plot Models

```{r}
custom_palette <- c(brewer.pal(9, "Set1"), brewer.pal(5, "Set2"))

line0h <- ggplot2::geom_hline(yintercept = 0, linetype = "dashed", color = "black", lwd = 0.125)
gg88 <- sjPlot::plot_models(
  fit.RT,
  fit.TP, fit.FP, fit.TN, fit.FN,
  fit.Accur,
  fit.Sensi,
  fit.Speci,
  fit.Preci,
  fit.FPR,
  fit.FNR,
  fit.FDR,
  fit.NPV,
  fit.FOR,
  m.labels = c(
    "fit.RT",
    "fit.TP", "fit.FP", "fit.TN", "fit.FN",
    "fit.Accur",
    "fit.Sensi",
    "fit.Speci",
    "fit.Preci",
    "fit.FPR",
    "fit.FNR",
    "fit.FDR",
    "fit.NPV",
    "fit.FOR"),
  legend.title = "Model",
  spacing=1,
  dot.size=1,
  # colors = viridis::viridis(14)
  colors = custom_palette
) + line0h +
  theme(
    text = element_text(size = 24),  # Increase base font size
    axis.title = element_text(size = 24),  # Axis titles
    axis.text = element_text(size = 22),  # Axis text
    legend.title = element_text(size = 24),  # Legend title
    legend.text = element_text(size = 22)  # Legend text
  ) + theme_minimal()

gg88
```

# Factor Reference Levels (reorder for comparison plots)

```{r}
df2 <- df0 %>%
  mutate(
    Ses = factor(Ses, levels=c("Morning", "Evening")),
    Run = factor(Run, levels=c("01", "02", "03")),
    Chrono = factor(Chrono, levels = c("Morning", "Evening")),
    Condit = factor(Condit, levels = c("Congruent", "Incongruent")),
  ) %>%
  mutate(
    NumBack = as.integer(NumBack),
    NumBack = paste0("n", sprintf("%02d", NumBack)),
    NumBack = factor(NumBack, levels = c("n01", "n02", "n03")),
  ) %>%
  identity()

df0 %>% dim()
df2 %>% dim()

REML <- TRUE
control <- lme4::lmerControl(optimizer = "Nelder_Mead")

fit.RT    = lmerTest::lmer(formula=RT    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.TP    = lmerTest::lmer(formula=TP    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FP    = lmerTest::lmer(formula=FP    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.TN    = lmerTest::lmer(formula=TN    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FN    = lmerTest::lmer(formula=FN    ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.Accur = lmerTest::lmer(formula=Accur ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Sensi = lmerTest::lmer(formula=Sensi ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Speci = lmerTest::lmer(formula=Speci ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.Preci = lmerTest::lmer(formula=Preci ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

fit.FPR   = lmerTest::lmer(formula=FPR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FNR   = lmerTest::lmer(formula=FNR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FDR   = lmerTest::lmer(formula=FDR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.NPV   = lmerTest::lmer(formula=NPV   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)
fit.FOR   = lmerTest::lmer(formula=FOR   ~ Ses + Chrono + Run + Condit + NumBack + (1 | Sub), data=df2, REML=REML, control=control)

```

# Settings

```{r}
options(ggeffects_margin = "mean_reference") ## DEFAULT
options(ggeffects_margin = "marginalmeans")
options(ggeffects_margin = "mean_mode")
options(ggeffects_margin = "empirical")
source("./helpers/helpers0.R")
```

# Check Models

## Check Model `fit.RT`

```{r}
model <- "fit.RT"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Chrono`

```{r}
extra <- "1001"
terms <- c("Chrono")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1002"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.TP`

```{r}
model <- "fit.TP"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run`

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1002"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.FP`

```{r}
model <- "fit.FP"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Condit`

```{r}
extra <- "1001"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1002"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

## Check Model `fit.TN`

```{r}
model <- "fit.TN"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Ses`

```{r}
extra <- "1001"
terms <- c("Ses")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit`

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

## Check Model `fit.FN`

```{r}
model <- "fit.FN"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run`

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit`

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.Accur`

```{r}
model <- "fit.Accur"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run`

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit`

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

## Check Model `fit.Sensi`

```{r}
model <- "fit.Sensi"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run`

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit`

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.Speci`

```{r}
model <- "fit.Speci"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` CAUTION - NS! (this should not be checked)

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` CAUTION - NS! (this should not be checked)

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.Preci`

```{r}
model <- "fit.Preci"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` 

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` 

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.FPR`

```{r}
model <- "fit.FPR"
fbase <- get_model_info(model, ofd0)
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.FNR`

```{r}
model <- "fit.FNR"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` 

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` 

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.FDR`

```{r}
model <- "fit.FDR"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` 

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` 

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.NPV`

```{r}
model <- "fit.NPV"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` 

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` 

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

## Check Model `fit.FOR`

```{r}
model <- "fit.FOR"
fbase <- get_model_info(model, ofd0)
```

### Effect of `Run` 

```{r}
extra <- "1001"
terms <- c("Run")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 

### Effect of `Condit` 

```{r}
extra <- "1002"
terms <- c("Condit")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### Effect of `NumBack`

```{r}
extra <- "1003"
terms <- c("NumBack")

suppressWarnings(rm(list = ls(pattern = "^ggeff")))
ggeff <- get_eff_null(model, terms, extra, ofd0)

cat0(sep0)
print(ggeff$pred0, n = Inf)
cat0(sep0)
print(ggeff$test0, n = Inf)
cat0(sep0)
print(ggeff$test2, n = Inf)
```

#### Plot Effect

```{r}
suppressWarnings(rm(list = ls(pattern = "^gg88")))
gg88 <- ggeff$pred0 %>% plot(limit_range=FALSE, show_data = FALSE, dot_alpha = 0.05)
gg88 <- gg88 # + timeD + lineE + lineT + lineR + rect3 ## + scaleA

ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.png"), plot = gg88, width=8, height=24)
ggsave(file = paste0(ggeff$fbasefig, "-pred0-fig.svg"), plot = gg88, width=16, height=48)

gg88
```

### 
